---
output:
  pdf_document: default
  html_document: default
---
title: "Netflix Data Analysis"
output: html_document
date: "2022-09-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Installing Libraries:

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(naniar)
library(forcats)
library(wordcloud)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(tidytext)
```

## Used head function to look at top 6 rows of data and read the data in.

```{r}
library(readxl)
netflix = read.csv("netflix_titles 2.csv")
```
## Used glimpse for summary.

```{r}
glimpse(netflix)
```

## Used summary for summary
```{r}
summary(netflix)
```

## Used separate function  to split date added column intop 2 columns

```{r}
netflix = netflix %>% separate(date_added,c("date_added", "year_added"), sep = ",")
```

```{r}
netflix = netflix %>% separate(listed_in, c("Category1", "Category2", "Category3"), sep = ",")
```
### Country column analysis 


```{r}
library(dplyr)
#Check how many NA values we have in the column
netflix = netflix %>% 
  mutate(country = ifelse(country == "", NA, country ))
 netflix %>% count(is.na(netflix$country), sort = TRUE)
 
 country <- drop_na(netflix, country) 
```

## We see top countries in Netflix based on the number of movies and tv shows

```{r}
country %>% group_by(country) %>% count(country, type) %>% arrange((desc(n))) %>% head(25)
```

### Data Visualization

Movies and tv shows over the years.

```{r}
ggplot(netflix, mapping = aes(x=release_year, fill = type)) +
geom_histogram(color = "black", binwidth=2)+
labs(title="Releases by Year")
```
```{r}
netflix %>%
count(is.na(netflix$country), sort = TRUE)
country_release <- drop_na(netflix, country)
country_release %>%
    count(country, sort = TRUE) %>%
    group_by(country) %>%
    head(25) %>%
    ggplot(aes(x=reorder(country, n), y=n, fill=country)) +
    geom_col(show.legend = FALSE) +
    labs(x="Sum of Movies and TV Shows Frequency", y="Movies and TV Shows Rleased", title="Top 25 Countries on Netflix") +
    coord_flip() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    geom_label(aes(label=n), show.legend=FALSE) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 3000))
```

```{r}
netflix %>%
 filter(!(rating %in% c("74 min", "84 min", "66 min", ""))) %>%
 ggplot() +
  aes(x = rating, fill = rating) +
  geom_bar() +
  scale_fill_hue(direction = 1) +
  labs(x = "Rating", y = "Count", title = "Rating by Type") +
  theme_minimal() +
  facet_wrap(vars(type)) +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
```{r}
desc_words_m <- netflix %>% select(type, show_id, description) %>%
  filter(type == "Movie") %>% 
    unnest_tokens(word, description) %>%
    anti_join(stop_words)
count_word <- desc_words_m %>%
   count(word, sort = TRUE)
wordcloud(words = count_word$word,  
          freq = count_word$n, 
          min.freq = 50,  
          max.words = nrow(count_word), 
          random.order = FALSE,  
          rot.per = 0.1,  
          colors = brewer.pal(8, "Dark2"))
```





